Global case

### 2025-05-09 lipschitz 2025/Lipitschz.tex
update

		The first case, $|x-y|\geq N\varepsilon$. Then we assume $|x-y| \in [M\varepsilon ,  (M+1)\varepsilon]$ for another integer $M\geq N$. Then we can divide the line segment between $x, y$ into $M+1$ pieces: $x_0 = x, x_1, x_2, \cdots, x_{M+1} = y$ such that $|x_i-x_{i+1}| \leq \varepsilon$ and apply the definition of $\varepsilon$-diff bound $D$ for each pieces:\begin{align*}
			|f(x)-f(y)| &= |f(x_{M+1})-f(x_M)+\cdots+f(x_1)-f(x_0)|\\
			&\leq |f(x_{M+1})-f(x_M)|+\cdots+|f(x_1)-f(x_0)|\\
			&\leq D\varepsilon + \cdots +D\varepsilon \\
			&= (M+1)D\varepsilon
		\end{align*}
		Hence\begin{align*}
			|f(x)-f(y)| &\leq (M+1)D\varepsilon \\
			&\leq D\cdot (M+1)\varepsilon \frac{|x-y|}{M\varepsilon}\\
			&= D\cdot\frac{M+1}{M} |x-y|\\
			&\leq   D\cdot\frac{N+1}{N} |x-y|
		\end{align*}
		The second case, $|x-y|< N\varepsilon$. Similarly we can divide the line segment between $x, y$ into $N$ pieces and then $|f(x)-f(y)|\leq D N\varepsilon\leq |f(x)-f(y)|\leq D \frac{N+1}{N} N\varepsilon$.

@@

@@

		Hence,\begin{align*}
			\dfrac{|f(x)-f(y)|}{|x-y|} &\leq \dfrac{Dx_1+Dx_2+\cdots+Dx_n}{x_1+x_2+\cdots+x_n -\frac{1}{N}\varepsilon}\\
			& = D\cdot( 1+  \dfrac{\frac{1}{N}\varepsilon}{x_1+x_2+\cdots+x_n -\frac{1}{N}\varepsilon})\\
			& \leq D\cdot( 1+  \dfrac{\frac{1}{N}\varepsilon}{\varepsilon})\\
			& = D \frac{N+1}{N} 
		\end{align*}

>>>>

		The first case, $|x-y|\geq N\varepsilon$. Then we assume $|x-y| \in [M\varepsilon ,  (M+1)\varepsilon]$ for another integer $M\geq N$. Then we can divide the line segment between $x, y$ into $M+1$ pieces: $x_0 = x, x_1, x_2, \cdots, x_{M+1} = y$ such that $|x_i-x_{i+1}| \leq \varepsilon$ and apply the definition of $\varepsilon$-diff bound $D$ for each pieces:\begin{align*}
			|f(x)-f(y)| &= |f(x_{M+1})-f(x_M)+\cdots+f(x_1)-f(x_0)|\\
			&\leq |f(x_{M+1})-f(x_M)|+\cdots+|f(x_1)-f(x_0)|\\
			&\leq D\varepsilon + \cdots +D\varepsilon = (M+1)D\varepsilon
		\end{align*}
		Hence,\begin{align*}
			|f(x)-f(y)| &\leq (M+1)D\varepsilon \leq D\cdot (M+1)\varepsilon \frac{|x-y|}{M\varepsilon}\\
			&= D\cdot\frac{M+1}{M} |x-y|	\leq   D\cdot\frac{N+1}{N} |x-y|		
		\end{align*}
		The second case, $|x-y|< N\varepsilon$. Similarly we can divide the line segment between $x, y$ into $N$ pieces and then $|f(x)-f(y)|\leq D N\varepsilon\leq |f(x)-f(y)|\leq D \frac{N+1}{N} N\varepsilon$.

@@

	In practice, Lipschitz above $\varepsilon$ constant is already sufficient, since in most cases we care about the absolute difference under input perturbations, not the ratio. By combining the above proposition, the computation of $\varepsilon$-diff bound can satisfy our aim.

	Moreover, we have one more proposition connecting $\varepsilon$-diff bound and Lipschitz above $\varepsilon$ constant.

@@

			Hence,\begin{align*}
			\dfrac{|f(x)-f(y)|}{|x-y|} &\leq \dfrac{Dx_1+Dx_2+\cdots+Dx_n}{x_1+x_2+\cdots+x_n -\frac{1}{N}\varepsilon}\\
			& \leq D\cdot( 1+  \dfrac{\frac{1}{N}\varepsilon}{\varepsilon})= D \frac{N+1}{N}\\
		\end{align*}
